\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-09 paper/main.tex
added new section on "Free recall of blocked versus random categorized word lists" along with a bunch of new refs

>>>>

\subsection*{Free recall of blocked versus random categorized word lists}

A large number of prior studies have compared participants' memories for
categorized word lists that are presented in blocked versus random orders. In
``blocked'' lists, all of the words from a given semantic category (e.g.,
animals) are presented consecutively, whereas in ``random'' lists, the words
from different categories are intermixed. Most of these studies report that
participants tend to better remember blocked (versus random)
lists~\citep{CofeEtal66, DAgo69, Dall64, Shap70, ShapPalm70, Kint70,
BoweEtal68, BoweEtal69, LuekEtal71}. Other studies suggest that these order
effects may also be modulated by factors like list length and the numbers of
examplars in each cateogry~\citep[e.g.,][]{BorgMang72}.

Although we did not directly manipulate ``blocking'' in our order manipulation
conditions, our sorting procedures in those conditions (see
\textit{Constructing feature-sorted lists}) have \textit{indirect} effects on
the lists' blockiness. For example, lists that are stochastically sorted by
semantic category will tend to contain runs of several same-category words in
succession. Consistent with the above work on blocked versus random categorized
lists, we found that participants tended to better remember lists that were
sorted semantically (Fig.~\ref{fig:barplots}B). However, this memory
improvement did not appear to extend to the other order manipulation conditions
we considered (e.g., to lexicographically or visually sorted lists). One
possibility is that the memory benefits of blocked versus random lists are
specific to semantic categories, and do not generalize to other feature
dimensions. Another possibility is that the memory benefits are due to the
presence of infrequent ``jumps'' between successive items (e.g., from different
categories). Because the features we manipulated in the lexicographic and
visual conditions were less categorical than the semantic features, feature
values across words in those conditions tended to vary more gradually.
Relatively stable features that are punctuated by infrequent large changes
(e.g., as words transition from a same-category sequence to a new category) may
also relate to perceived ``event boundaries,'' which can have important
consequences for memory~\citep{RadvZack17, DuBrEtal17, DuBrDava16, DuBrDava13}.
